---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

Scientifically, this was a straightforward project to reproduce.  The
authors had provided a github repository containing their Rmarkdown
file to generate the paper, along with all data required.  The authors
had also clearly enumerated which R packages were required.

The only significant problem was that one of the CRAN R packages (gt)
used was troublesome to work correctly on Ubuntu 23.10, which
required significant workarounds as described below.

\clearpage

# CODECHECKER notes


Using a recent install of Ubuntu 23.10 on a 2018 laptop, I needed to include some extra
system packages to start the codecheck process.

    sudo apt install libsodium-dev
    sudo apt install librdf0-dev
    sudo apt install librsvg2-dev  # for rsvg package
    sudo apt install libmagick++-dev  # magick package
    sudo apt install chromium-browser # for gt
    sudo apt install texlive-xetex  ## needed for xelatex


then we could proceed, installing codecheck

    install_github('codecheckers/codecheck')

    require(codecheck)
    create_codecheck_files()


First, I needed to install the packages as outlined in their file
`install_packages.R`.  This took about an hour to complete on my
laptop.

Although all packages installed, once compiling the Rmarkdown, I hit
two problems with the gt package.  First, it only seemed to work
within Rstudio, rather than in Emacs terminal.  Second, the gt package
was unable to convert html output to png.  This has been documented
online as a problem, and remains an open issue: <https://github.com/rstudio/gt/issues/1029>



Figure 1 is a drawio file, not computed, but generated from the
website <https://drawio.com> using the file `LEBA_figure1.drawio` provided
in the Figures folder.  When I loaded this .drawio file into the web,
it generated Figure1.png.  I could not find the source for Figure 5.
Otherwise, all figures were reproduced, although I needed to edit the
Rmarkdown file to save tables as html, rather than png, using:

     ##gtsave("Figures/Figure2.png", vwidth=6000)
     gtsave('Figures/Figure2.html') #sje

After the code had run, there were some issues generating the final
pdf manuscript, namely the lack of apa6.cls and Arial font.

The html tables generated were output were loaded into a browser and
then screenshots of the tables were taken for inclusion here.

## Notes

1. None of the 'classic' tables were reproduced due to the issues with
the latex document not compiling.

## Recommendations


* There is no .rproj file, unlike suggested in the readme; provide one
  or delete reference to it.
* LaTeX requirements (apa6.cls and Arial font) should be adjusted to
  make them more portable.
* There is not much that could be done about the problems with the gt
  package; the authors report it working well on Mac.  However, this
  could be documented.
* I'd suggest removing the code chunk (that is not run by default) to
  install packages, and instead ensure everytyhing is listed in  the
  `install_packages.R` file.  (Some items were missing, that are
  documented in my copy of the file.
* Include a final code chunk in your Rmarkdown file that calls
  `sessionInfo()` to list the R environment used to generate your
  file.  You can see an example at the end of this document.
* The main figure numbers in the filenames match that used in the
  code; there is an 'off by one' error in the figure numbers used in
  the manuscript versus the numbers in the files.  This could be
  fixed in any future versions.

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

I would like to thank Dr Spitschan and his team for promptly answering
any queries I had with this reproduction.  CODECHECK is financially
supported by the Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
<!-- https://doi.org/10.5281/zenodo.10213244 was given by system; so -->
<!-- subtract 1 to guess permanent DOI -->
